### 2020-01-10 paper/introduction.tex
Ready for Andrei's review before proofreading

At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is quite large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling,
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

>>>>

At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
fuel than that required to achieve criticality (necessary for long-term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

### 2020-01-10 paper/results.tex
Ready for Andrei's review before proofreading

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
calculation), when all CRs are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
Additionally, the previously studied $^{233}$U case recorded the maximum reactivity
during 60 effective full-power years (EFPY) of reactor operation to be 
$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25}).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

@@

The total worth of all control rods ranges from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
$\$$ (Table~\ref{tab:worth}). B$_4$C-90 (boron is enriched to 90\% $^{10}$B) 
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorbing materials in this study. This 
result agrees with macroscopic absorption cross sections data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The control rod material are being transmuted during 
operation. The effect of the fuel salt burnup on the control rod worth is not 
considered herein, and will be investigated and presented in Part II of this 
study.

As shown in Table~\ref{tab:worth}, the worth of the CSD clusters is by factor $1.56$ greater than 
the worth of the SSD system for all absorbing materials. Either CSD or SSD 
clusters are able to shut down the reactor initially loaded by 
$^{233}$U and reactor-grade Pu regardless of the absorbing material type. 
However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
initially loaded with transuranic (TRU) elements. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU \cite{ashraf2020Strategies}.

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), where the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
the worth almost equal to the worth of all other CRs together regardless of 
the absorbing material type (Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
greater than in fast spectrum.

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD cannot compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and transuranic 
(TRU) elements. However, the outer ring of the CSD worth is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U .

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters to 
investigate the variation of CRW with the position in the active core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$), consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core. As mentioned previously, the CRs 
absorption ability degrades in fast spectrum.

@@

\begin{table}  [!hb]
	\caption{The shutdown margins for the SD-TMSR core for different absorbing materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ &$1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.8\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.12\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.89\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. The strongest anti-shadowing effect has occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
The obtained results emphasize that there is no relation between the absorbing
materials type and the interference between the control rod clusters
(i.e., the amplification factor (A$_{CRi}$)).

Insertion of the control rod affects the neutron flux distribution, which is 
the primary reason for the amplification of CR worths indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CRs position: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as absorbing materials because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape in certain positions, i.e., around CRs 
positions. This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CRs positions.} 
	\label{fig:totalflux}
\end{figure}

@@

The integral and differential control rod worth are calculated for three 
different systems: all control rods, CSD, and SSD systems. The CRs are 
inserted gradually into the core from the top to the bottom. 
Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
differential CRW, respectively. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
clusters are about $48.39$ $\$$, $25.3$ $\$$, and $16.46$ $\$$, respectively. The 
integral worth of SSD clusters is sufficient to shut down the reactor from any 
state.

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
materials in this study. Notably, all result are based on steady state calculations.

>>>>

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
calculation), when all CRs are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are $1.65\pm0.04$ 
$\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, respectively.
The previously studied $^{233}$U case recorded the maximum reactivity
during 60 effective full-power years (EFPY) of reactor operation to be 
$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25}).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

@@

The total worth of all control rods extends from $33.7\pm0.4$ $\$$ to $48.19\pm0.68$ 
$\$$ (the first row in Table~\ref{tab:worth}). B$_4$C-90 $-$ boron enriched to 90\% $^{10}$B $-$
has the largest absorption ability, while Gd$_2$O$_3$ has the lowest 
absorption compared with the other absorbing materials in this study. This 
result agrees with macroscopic absorption cross sections data 
\cite{guo2019optimized}. B$_4$C-90 has the highest macroscopic 
absorption cross sections followed by Eu$_2$O$_3$, HfB$_2$, HfH$_{1.62}$, and 
finally Gd$_2$O$_3$. The control rod material is being transmuted during 
operation. The effect of the fuel salt burnup on the control rod worth is neglected
herein, and will be investigated and presented in Part II of this 
study.

The worth of the CSD clusters is by factor $1.56$ greater than 
the worth of the SSD system for all absorbing materials. Either CSD or SSD 
clusters are able to shut down the reactor initially loaded by 
$^{233}$U and reactor-grade Pu regardless of the absorbing material type because 
the $\rho_e$ for $^{233}$U and reactor-grade Pu as initial fissile material are $1.65\pm0.04$ 
$\$$ and $4.11\pm0.02$ $\$$, respectively. However, only SSD clusters made of B$_4$C-90 are able to shut down the SD-TMSR 
initially loaded with transuranic (TRU) elements ($\rho_e$ is $15.38\pm0.04$ $\$$). The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU \cite{ashraf2020Strategies}.

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
the worth almost equal to the worth of all other CRs together regardless of 
the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of incident neutron, for example, boron absorbs neutrons in thermal spectrum much 
greater than in fast spectrum.

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and transuranic 
(TRU) elements. However, the outer ring of the CSD worth is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

We separately calculated the worth of CSD2, CSD9, SSD1, and SSD4 clusters to 
investigate the variation of CRW with the position in the inner core.
The CRW decreases in the direction of the outer core zone. The outer core zone 
has smaller moderator-to-fuel ratio ($0.86$) compared with the central zone 
($2.8$), consequently, the neutron energy spectrum is faster in the peripheral 
zone than in the center of the core. As mentioned previously, the CRs 
absorption ability degrades in fast spectrum.

@@

\begin{table}  [!hb]
	\caption{The shutdown margins for the SD-TMSR core for different absorbing materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Absorbing materials        				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		B$_4$C-90                          & $14.74\pm0.09$ $\$$ & $12.28\pm0.12$ $\$$ & $ $ $ $ $1.01\pm0.09$ $\$$ \\
		Eu$_2$O$_3$                       &  $12.93\pm0.09$ $\$$    &  $10.47\pm0.12$ $\$$   &$-0.80\pm0.09$ $\$$\\
		HfB$_2$        				 &$12.62\pm0.24$ $\$$ &$10.16\pm0.26$ $\$$ &$-1.11\pm0.24$ $\$$   \\
		HfH$_{1.62}$							& $11.58\pm0.19$ $\$$ &$9.120\pm0.22$ $\$$ &$-2.15\pm0.19$ $\$$ \\
		Gd$_2$O$_3$	  		& $10.35\pm0.22$ $\$$ &$7.890\pm0.25$ $\$$& $-3.38\pm0.22$ $\$$\\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. The strongest anti-shadowing effect has occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratio (see Table~\ref{tab:worth}).
The obtained results emphasize that no relation between the absorbing
materials type and the interference between the control rod clusters
(i.e., the amplification factor (A$_{CRi}$)).

Insertion of the control rod affects the neutron flux distribution, which is 
the primary reason for the amplification of CR worths indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CRs position: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as absorbing materials because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape in certain positions, i.e., around CRs 
positions. This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core \cite{girardin2007control}.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CRs positions.} 
	\label{fig:totalflux}
\end{figure}

@@

The integral and differential control rod worths are calculated for three 
different systems: all control rods, CSD, and SSD systems. The CRs are 
inserted gradually into the core from the top to the bottom. 
Equation~\ref{Equ:4} and~\ref{Equ:5} are used to calculate the integral and 
differential CRW, respectively. Figure~\ref{fig:integ} illustrates the integral CRW for CRs 
made of B$_4$C-90. The maximum integral worth of All CRs, CSD, and SSD 
clusters are about $48.39$ $\$$, $25.3$ $\$$, and $16.46$ $\$$, respectively. The 
integral worth of SSD clusters is sufficient to shut down the reactor from any 
state.

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with five 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
materials in this study. Notably, all results are based on steady state calculations.
